\textbf{Characterizing Errors and Uncertainties in NEMD Simulations of Phonon Transport}

### 2018-04-11 Slides/r1/md_si.tex
..

%% General document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{decorations.fractals}
%\usepackage{lmodern}
\usepackage{animate}
\usepackage{movie15}
\usepackage{bm}
\usepackage{pifont}
\usepackage{empheq}
\usepackage[many]{tcolorbox}
\usepackage{smartdiagram}
\usepackage[customcolors]{hf-tikz}
\usepackage{dashrule} % for dotted vertical line
%\usepackage{flexisym}

@@

%\subtitle{SUBTITLE}
\author[M. Vohra and S. Mahadevan]{Manav Vohra$^{\dag}$, Sankaran Mahadevan$^{\dag}$ \\ \vspace{2mm}
\scriptsize{Collaborators: Seungha Shin$^{\S}$, Ali Yousefzadi Nobakht$^{\S}$}}
\vspace{-1mm}
\institute{$^{\dag}$Vanderbilt University\\ \vspace{1mm}
$^{\S}$University of Tennessee, Knoxville}

@@

>>>>

%% General document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{decorations.fractals}
%\usepackage{lmodern}
\usepackage{animate}
\usepackage{movie15}
\usepackage{bm}
\usepackage{pifont}
\usepackage{empheq}
\usepackage[many]{tcolorbox}
\usepackage{smartdiagram}
\usepackage[customcolors]{hf-tikz}
\usepackage{dashrule} % for dotted vertical line
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{pigment}{rgb}{0.2, 0.2, 0.6}
%\usepackage{flexisym}

@@

%\subtitle{SUBTITLE}
\author[M. Vohra and S. Mahadevan]{Manav Vohra$^{\dag}$, Sankaran Mahadevan$^{\dag}$ \\ \vspace{2mm}
\scriptsize{Collaborators: Seungha Shin$^{\S}$, Ali Y. Nobakht$^{\S}$}}
\vspace{-1mm}
\institute{$^{\dag}$Vanderbilt University\\ \vspace{1mm}
$^{\S}$University of Tennessee, Knoxville}

@@

\section{\scshape Background}
\subsection{bg}

\begin{frame}{Non-Equilibrium MD}

\begin{itemize}

\myitem Widely used to study thermal (phonon) transport in 
{\color{pigment}non-metallic} systems (C,Si,Ge).
\vspace{2mm}
\myitem System subjected to a temperature gradient using thermostats.
\vspace{2mm}
\myitem {\color{pigment}Steady-state} thermal energy exchange between
the thermostats is used in Fourier's law to estimate bulk thermal
conductivity~($\kappa$). \vspace{2mm}
\myitem Estimates are {\color{pigment}uncertain} and severely
{\color{pigment}under-predicted}.
\begin{itemize}
  \item Simulation length-scales $\ll$ phonon mean free path. \vspace{1mm}
  \item Thermostats reduce correlation b/w vibration modes.
\end{itemize}

\end{itemize}

\end{frame}

\subsection{bg}

\begin{frame}{Sources of Uncertainty}

\begin{columns}
\begin{column}{0.52\textwidth}

\begin{itemize}
\myitem Bulk thermal conductivity is size-dependent.
\vspace{2mm}
\myitem Variability in applied thermal gradient~(Kapitza~effect).
\vspace{2mm}
\myitem Choice of the inter-atomic potential.
\vspace{2mm}
\myitem Nominal estimates of the potential parameters.

\end{itemize}
\end{column}

\begin{column}{0.48\textwidth}

\begin{center}
\begin{figure}[htbp]
\vspace{-3mm}
  \includegraphics[width=0.9\textwidth]{./Figures/cond_size}
  \\ \vspace{2mm}
  \includegraphics[width=0.9\textwidth]{./Figures/temp_plot}
\end{figure}
\end{center}

\end{column}
\end{columns}

\end{frame}

\subsection{bg}

\begin{frame}{Specific Research Goals}

\begin{itemize}

\myitem Quantify discrepancy in $\kappa$ between predictions and data.
\begin{itemize}
\item Construct a response surface for $\kappa(s,\frac{d\theta}{dx})$.
\end{itemize}
\vspace{2mm}
\myitem Perform sensitivity analysis of the potential parameters.
\begin{itemize}
\item Estimate derivative-based sensitivity measures~(DGSM).
\end{itemize}
\vspace{2mm}
\myitem Construct a reduced order surrogate for $\kappa$ using sparse
NEMD predictions.
\begin{itemize}
\item Use the surrogate for forward propagation of uncertainty, and global
sensitivity analysis. 
\end{itemize}
\vspace{2mm}
\myitem Calibrate the \textit{important} parameters in a Bayesian setting.

\end{itemize}

\end{frame}

\section{\scshape Set-up}
\subsection{setup}

\begin{frame}{Problem Set-up}

\begin{columns}
\begin{column}{0.5\textwidth}

\begin{center}
\begin{tikzpicture}
\node[fill=white,inner sep=0pt] 
{\rowcolors{1}{DeepSkyBlue!20}{DeepSkyBlue!5}
	\resizebox{\columnwidth}{!}{
  \begin{tabular}{l|c}
%\hline
	Lattice Constant, $a$ ($\angstrom$) & 5.43 \\ 
	Width, Height ($\angstrom$) & 22$a$ \\ 
	$\Delta t$  (ps) & 0.0005 \\
	Boundary Condition & Periodic \\ 
	Lattice Structure & Diamond \\ 
	Inter-atomic Potential & Stillinger-Weber

%\hline
  \end{tabular}%
	}
};
\end{tikzpicture}
\end{center}

\end{column}

\begin{column}{0.5\textwidth}

%\vspace{-5mm}
\begin{center}
\begin{figure}[htbp]
        \includegraphics[width=0.9\textwidth]{./Figures/schematic}
\end{figure}
\vspace{3mm}
%        \animategraphics[autopause,poster=first,loop,height=0.60\textwidth]{5}
%        {./animation/snap}{0}{64}
\end{center}
\end{column}
\end{columns}

\end{frame}

\subsection{setup}
\begin{frame}{Problem Set-up}

%\vspace{-4mm}

\begin{itemize}
\myitem \textsc{Stages}:\\

\begin{center}
{\color{green}NVT} \hspace{5mm} $\rightarrow$ \hspace{5mm} {\color{cyan}NVE} \hspace{5mm}
$\rightarrow$ \hspace{5mm} {\color{magenta}NVE}
\\ \vspace{1mm}
\tiny \hspace{-5mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
 [Generate Data]
\\ \vspace{1mm}

\tiny{N: Number of Atoms~~~V: Volume~~~T: Temperature~~~E: Energy}
\end{center}

\normalsize

\myitem \textsc{Observable}: Avg. energy exchange b/w thermostats~($q$)
\vspace{2mm}

\myitem \textsc{QoI}: Bulk thermal conductivity ($\kappa$)

\begin{empheq}[box=\tcbhighmath]{align}
  \kappa = \frac{q}{\left|\frac{dT}{dx}\right|} \nonumber
\end{empheq}

\vspace{2mm}

\myitem Appropriate selection of {\color{pigment}width}, 
{\color{pigment}height}, and {\color{pigment}simulation-time} was ensured.  
\end{itemize}

\end{frame}

\section{\scshape Discrepancy}
\subsection{response}
\begin{frame}{Response Surface: Discrepancy}

\begin{columns}
\begin{column}{0.52\textwidth}

\begin{itemize}
\myitem PC representation of the discrepancy, 
$\epsilon_{\mbox{\tiny{d}}}$:

\begin{empheq}[box=\tcbhighmath]{align}
\epsilon_{\mbox{\tiny{d}}} \approx \mathcal{\epsilon}_{\mbox{\tiny{d}}}^{\mbox{\tiny{PCE}}} = 
\sum_{\bm{k}\in\mathcal{I}} c_{\bm{k}}(T)\Psi_{\bm{k}}(\bm{\xi(\theta)})
\nonumber
\end{empheq}

\end{itemize}
\end{column}

\begin{column}{0.48\textwidth}

\begin{center}
\begin{figure}[htbp]
\vspace{-3mm}
  \includegraphics[width=0.95\textwidth]{./Figures/realz_quad300K}
  \\ \vspace{1mm}
  \includegraphics[width=0.9\textwidth]{./Figures/PCspectrum_300}
\end{figure}
\end{center}

\end{column}
\end{columns}

\end{frame}
